Appendix

### 2020-03-06 manuscript/appendix.Rmd
adjust figure captions
add tile drainage plot

```{r trophic_state, fig.cap="Lake trophic state in our study lakes versus all lakes from Soranno et al. (2017) located with our study extent. Trophic state based on the chlorophyll critera from Carlson (1996)", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}

@@

>>>>

```{r trophic_state, fig.cap="Lake trophic state in our study lakes versus all lakes from Soranno et al. (2017) located within our study extent. Trophic state based on the chlorophyll critera from Carlson (1996)", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}

@@

```{r tile_drainage_vs_clay, fig.cap = "Scatterplot showing the median clay content of watersheds in our hydrologic regions plotted against percent tile drainage from Nakagaki and Wieczorek (2016). Our regions highly sensitive to agriculture land-use from Figure 4 are highlighted.", warning=FALSE, echo = FALSE, eval=TRUE, fig.height=3, fig.width=3.3}
# load huc4 clay estimates
signif_hu4_ids <- c("HU4_56", "HU4_57")
dt <- readRDS("../data/dt.rds") %>%
  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
  dplyr::select(lagoslakeid, hu4_zoneid, clay_pct, signif_hu4) %>%
  group_by(hu4_zoneid) %>%
  mutate(median = median(clay_pct, na.rm = TRUE)) %>%
  distinct(hu4_zoneid, median, signif_hu4)

# compute per huc tile drainage
# load huc4s
# study_bbox    <- st_read("data/gis.gpkg", "study_bbox", quiet = TRUE)[3,]
# hu4_focal     <- st_read("data/gis.gpkg", "hu4s_focal_simple", quiet = TRUE)
# hu4_focal     <- st_crop(st_transform(hu4_focal, st_crs(study_bbox)), study_bbox)
# http://dx.doi.org/10.5066/F7W37TDP
# library(exactextractr)
# r <- raster("data/SubsurfaceDrainExtentMW_2012.tif")
# test <- st_cast(hu4_focal, "MULTIPOLYGON")
# test$tile_drainage <- exact_extract(r, test, "sum")
# saveRDS(test, "data/tile_drainage.rds")
test <- readRDS("../data/tile_drainage.rds")
test2 <- left_join(test, dt, by = c("ZoneID" = "hu4_zoneid"))

# scatter plot clay versus tile drainage highlighting sensitve hucs
ggplot(data = test2) +
  geom_point(aes(x = tile_drainage/900, # grid cells are 30x30 = 900
                 y = median, color = signif_hu4)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  xlab("Percent tile drainage") + ylab("Median clay content (percent)") +
  cowplot::theme_cowplot() +
  theme(legend.position = c(0.6, 0.3), 
        legend.background = element_rect(fill = "white", color = "black"),
        legend.text = element_text(size = 10), 
        legend.title = element_text(size = 11)) +
  labs(color = "LULC Sensitive")
```
